Model LF

### 2022-10-05 Estimation.Rmd
Commit

@@

@@

```{r}
reg_part_start=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),1:4) +  L(TSDELTALOG(komp_r_obs1),0:4)+  L(TSDELTALOG(rw_ds),0:4) + L(TSDELTA(ur_ds),0:4)+ L(log(part1),1) + L(log(komp_r_obs1),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs1), 0:4)", c(1,4))
 part_vars_1 <- str_c("L(TSDELTALOG(part1), 1:4)", c(1,3,4))
 rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(0,2,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(0,1,2,4))
```

@@

```{r}
reg_part=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),c(2)) +  L(TSDELTALOG(komp_r_obs1),c(0,2,3))+  L(TSDELTALOG(rw_ds),1) + L(log(part1),1) + L(log(komp_r_obs1),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

>>>>

```{r}
arpdiag <- function(series, lags) {
x <- mat.or.vec(lags, 1)
y <- mat.or.vec(lags, 1)
y <- y + 0.05
for (i in 1:lags) {
x[i] <- Box.test(series, lag = i, type = "Ljung-Box")$p.value
}
plot(x, xlab = "Lags", ylab = "p-value H0: no
Autocorrelation", type = "p",
main = "Ljung-Box Test for
Autocorrelation", ylim = c(0, 1))
axis(1, 1:lags)
abline(0.05, 0, lty = 2, col = "blue")
}
```

@@

### kont_h

```{r}
kont_h_dp_person=kont_h/ mean_dp_regul
```

```{r}
model_start_kont_h <- dynlm(diff(kont_h_dp_person) ~ 1+ L(kont_h_dp_person, 1) + L(diff(kont_h_dp_person), c(1,5,9)))
summary(model_start_kont_h)
```

```{r}
urca_komp_r= ur.df(kont_h_dp_person, lags = 4, type = "trend")
summary(urca_komp_r)
```

```{r}
diff_kont_h=diff(kont_h_dp_person)
```

```{r}
urca_diff_kont_h= ur.df(diff_kont_h, lags = 3, type = "none")

summary(urca_diff_kont_h)
```

```{r}
res_kont_h= urca_diff_kont_h@testreg$residuals
arpdiag(res_kont_h, 12)
```

Kontanthjælp is I(1)

@@

```{r}
reg_part_start=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),1:4) +  L(TSDELTALOG(kont_h_dp_person),0:4)+  L(TSDELTALOG(rw_ds),0:4) + L(TSDELTA(ur_ds),0:4)+ L(log(part1),1) + L(log(kont_h_dp_person),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
 komp_r_vars_1 <- str_c("L(TSDELTALOG(kont_h_dp_person), 0:4)", c(0,2,3,4))
 part_vars_1 <- str_c("L(TSDELTALOG(part1), 1:4)", c(1,4))
 rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(1,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(1,2,3,4))
```

@@

```{r}
reg_part=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),2:3) +  L(TSDELTALOG(kont_h_dp_person),1)+  L(TSDELTALOG(rw_ds),c(0,2,3)) + L(TSDELTA(ur_ds),c(0))+ L(log(part1),1) + L(log(kont_h_dp_person),1) + L(log(rw_ds),1) + L((ur_ds),1) )

### 2022-10-05 max_dp endogen stød.Rmd
Commit

@@

BEHAVIORAL> part1
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part1,2)) + beta_3*TSDELTALOG(komp_r) +beta_4*TSDELTALOG(TSLAG(komp_r,2)) + beta_5*TSDELTALOG(TSLAG(komp_r,3)) +beta_6*TSDELTALOG(TSLAG(rw_ds,1))  + beta_9*LOG(TSLAG(part1,1))  + beta_10*log(TSLAG(rw_ds,1)) + beta_11*log(TSLAG(komp_r,1)) + beta_12*TSLAG(ur_ds,1) + beta_13* d_2013q4
COEFF> beta_0 beta_1 beta_3 beta_4 beta_5 beta_6 beta_9 beta_10 beta_11 beta_12 beta_13
STORE> coe(16)

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$sens2 = sens2

@@

shock_kuld_00 = S_model$simulation$shock_kuld

@@

@@

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr
u_ds_01b = Shock_1b$simulation$u_ds
part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person

@@

plot(dp_person_01b, col= "red"); lines(dp_person_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

@@

i_equip_nfc_k_ds_05 = Shock_5$simulation$i_equip_nfc_k_ds
u_ds_05 = Shock_5$simulation$u_ds
wage_gap1_05 = Shock_5$simulation$wage_gap1
gk_05 = Shock_5$simulation$gk

@@

@@

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h
dp_person_06 = Shock_6$simulation$dp_person
part1_06 = Shock_6$simulation$part1
u_ds_06 = Shock_6$simulation$u_ds

@@

plot(u_ds_06, col= "red"); lines(u_ds_05, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

@@

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.998,1.0015));
lines((yk_ds_05 / yk_ds_00), col= "blue");
lines((yk_ds_06 / yk_ds_00), col= "green");
lines((yk_ds_07 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

>>>>

 #kontanthjælp
kont_h= kont_h/1000
kont_h_dp_person=kont_h/mean_dp_regul

@@

BEHAVIORAL> part1
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part1,2)) + beta_2*TSDELTALOG(TSLAG(part1,3)) +beta_3*TSDELTALOG(TSLAG(kont_h_ratio,1)) +beta_4*TSDELTALOG(rw_ds)  +beta_5*TSDELTALOG(TSLAG(rw_ds,2)) +beta_6*TSDELTALOG(TSLAG(rw_ds,3))  + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(kont_h_ratio,1)) + beta_11*TSLAG(ur_ds,1)
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_5 beta_6 beta_8 beta_9 beta_10 beta_11 
STORE> coe(16)

COMMENT> 
IDENTITY> kont_h_ratio
EQ> kont_h_ratio = kont_h / dp_person

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$kont_h_ratio = kont_h_dp_person

@@

shock_kuld_00 = S_model$simulation$shock_kuld
kont_h_ratio_00 = S_model$simulation$kont_h_ratio

@@

plot(kont_h_ratio_00, col= "green"); lines(kont_h_dp_person, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr
u_ds_01b = Shock_1b$simulation$u_ds
part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person
kont_h_ratio_01b = Shock_1b$simulation$kont_h_ratio

@@

plot(dp_person_01b, col= "red"); lines(dp_person_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_01b, col= "red"); lines(kont_h_ratio_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

```{r}
shock_wage_ds_model_shock=shock_wage_ds_model %>% window(start= c(2016,1))
```

@@

i_equip_nfc_k_ds_05 = Shock_5$simulation$i_equip_nfc_k_ds
u_ds_05 = Shock_5$simulation$u_ds
wage_gap1_05 = Shock_5$simulation$wage_gap1
gk_05 = Shock_5$simulation$gk
kont_h_ratio_05 = Shock_5$simulation$kont_h_ratio

@@

```{r}
shock_part_model_shock=shock_part_model %>% window(start= c(2016,1))
```

@@

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h
dp_person_06 = Shock_6$simulation$dp_person
part1_06 = Shock_6$simulation$part1
u_ds_06 = Shock_6$simulation$u_ds
kont_h_ratio_06 = Shock_6$simulation$kont_h_ratio
```

@@

plot(u_ds_06, col= "red"); lines(u_ds_05, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_06, col= "red"); lines(kont_h_ratio_05, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

```{r}
shock_kuld_model_shock=shock_kuld_model %>% window(start= c(2016,1))
```

@@

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.998,1.001));
lines((yk_ds_05 / yk_ds_00), col= "blue");
lines((yk_ds_06 / yk_ds_00), col= "green");
lines((yk_ds_07 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```
